Equations & R Code

### 2017-03-24 manuscript/coexistence-stability_ms.Rmd
fixes annoying typos and updates R equation

Fluctuating environmental conditions are an important ingredient for stable species coexistence, both in theoretical models [@Chesson2000; @Chesson2004] and in natural communities [@Caceres1997; @Descamps-Julien2005; @Adler2006; @Angert2009].
Such "fluctuation-dependent" coexistence \new{emerges most easily when} species have unique environmental responses and that environmental conditions vary so that each species in a community experiences favorable and unfavorable conditions, which prevents competitive exclusion [@Chesson2000].
\new{Chesson (2000) described the two fluctuation-dependent mechanisms: the storage effect and relative nonlinearity.
Both mechanisms operate when environmental variation favors different species at different times. 
Under the storage effect, this happens because species are competing for resources at different times (and escaping competition in unfavorable periods). 
Under relative nonlinearity, all species are competing for resources at the same time, but each species alters resource availability in a way that favors its competitors.
We describe these mechanisms in more detail below (see \textbf{Materials and Methods: Consumer-resource model}).}

@@

We assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource pool (*R*) at the start of the growing season is $R_{\tau(0)} = R^+$, where $R^+$ is a random resource pulse drawn from a log-normal distribution with mean $\mu(R^+)$ and standard deviation $\sigma(R^+)$. 
\new{Taken all together, we can combine equations 1 and 4 to define the discrete transitions between live and dormant biomass at the end of a growing season.
Thus, the initial conditions for each state ($D, N, R$) at the beginning of growing season $\tau+1$ are:}
\vspace{-3em}
\begin{align}
  D_{i,\tau(0) + 1} &= (1-\gamma_{i,\tau}) \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  N_{i,\tau(0) + 1} &= \gamma_{i,\tau} \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  R_{\tau + 1} &= \text{lognormal}\left(\mu(R^+), \sigma(R^+) \right)_0^{200},
\end{align}
\vspace{-3em}
\noindent \new{where, as above, $\tau(T)$ denotes the end of growing season $\tau$ and $\tau(0) + 1$ denotes the beginning of growing season $\tau+1$.} 
\new{The subscript (0) and superscript (200) indicates a lognormal distribution truncated at those values.
We used the function \texttt{urlnorm} from the "Runuran" package} [@Leydold2015] \new{to generate values from the truncated lognormal distribution.}
Model parameters and notation are described in Table 1.

>>>>

Fluctuating environmental conditions are an important ingredient for stable species coexistence, both in theoretical models [@Chesson2000; @Chesson2004] and in natural communities [@Caceres1997; @Descamps-Julien2005; @Adler2006; @Angert2009].
Such "fluctuation-dependent" coexistence \new{emerges most easily when} species have unique environmental responses and environmental conditions vary so that each species in a community experiences favorable and unfavorable conditions, which prevents competitive exclusion [@Chesson2000].
\new{Chesson (2000) described the two fluctuation-dependent mechanisms: the storage effect and relative nonlinearity.
Both mechanisms operate when environmental variation favors different species at different times. 
Under the storage effect, this happens because species are competing for resources at different times (and escaping competition in unfavorable periods). 
Under relative nonlinearity, all species are competing for resources at the same time, but each species alters resource availability in a way that favors its competitors.
We describe these mechanisms in more detail below (see \textbf{Materials and Methods: Consumer-resource model}).}

@@

We assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource pool (*R*) at the start of the growing season is $R_{\tau(0)} = R^+$, where $R^+$ is a random resource pulse drawn from a log-normal distribution with mean $\mu(R^+)$ and standard deviation $\sigma(R^+)$. 
\new{Taken all together, we can combine equations 1 and 4 to define the discrete transitions between live and dormant biomass at the end of a growing season.
Thus, the initial conditions for each state ($D, N, R$) at the beginning of growing season $\tau+1$ are:}
\vspace{-3em}
\begin{align}
  D_{i,\tau(0) + 1} &= (1-\gamma_{i,\tau}) \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  N_{i,\tau(0) + 1} &= \gamma_{i,\tau} \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  R_{\tau(0) + 1} &= \text{lognormal}\left(\mu(R^+), \sigma(R^+) \right)_0^{200},
\end{align}
\vspace{-3em}
\noindent \new{where, as above, $\tau(T)$ denotes the end of growing season $\tau$ and $\tau(0) + 1$ denotes the beginning of growing season $\tau+1$.} 
\new{The subscript (0) and superscript (200) indicates a lognormal distribution truncated at those values.
We used the function \texttt{urlnorm} from the "Runuran" package} [@Leydold2015] \new{to generate values from the truncated lognormal distribution.}
Model parameters and notation are described in Table 1.

### 2017-03-24 manuscript/coexistence-stability_ms.tex
fixes annoying typos and updates R equation

Fluctuating environmental conditions are an important ingredient for
stable species coexistence, both in theoretical models (Chesson 2000a;
Chesson et al. 2004) and in natural communities (Cáceres 1997;
Descamps-Julien \& Gonzalez 2005; Adler et al. 2006; Angert et al.
2009). Such ``fluctuation-dependent'' coexistence
\new{emerges most easily when} species have unique environmental
responses and that environmental conditions vary so that each species in
a community experiences favorable and unfavorable conditions, which
prevents competitive exclusion (Chesson 2000a).
\new{Chesson (2000) described the two fluctuation-dependent mechanisms: the storage effect and relative nonlinearity.
Both mechanisms operate when environmental variation favors different species at different times. 
Under the storage effect, this happens because species are competing for resources at different times (and escaping competition in unfavorable periods). 
Under relative nonlinearity, all species are competing for resources at the same time, but each species alters resource availability in a way that favors its competitors.
We describe these mechanisms in more detail below (see \textbf{Materials and Methods: Consumer-resource model}).}

@@

\begin{align}
  D_{i,\tau(0) + 1} &= (1-\gamma_{i,\tau}) \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  N_{i,\tau(0) + 1} &= \gamma_{i,\tau} \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  R_{\tau + 1} &= \text{lognormal}\left(\mu(R^+), \sigma(R^+) \right)_0^{200},
\end{align}\vspace{-3em}

>>>>

Fluctuating environmental conditions are an important ingredient for
stable species coexistence, both in theoretical models (Chesson 2000a;
Chesson et al. 2004) and in natural communities (Cáceres 1997;
Descamps-Julien \& Gonzalez 2005; Adler et al. 2006; Angert et al.
2009). Such ``fluctuation-dependent'' coexistence
\new{emerges most easily when} species have unique environmental
responses and environmental conditions vary so that each species in a
community experiences favorable and unfavorable conditions, which
prevents competitive exclusion (Chesson 2000a).
\new{Chesson (2000) described the two fluctuation-dependent mechanisms: the storage effect and relative nonlinearity.
Both mechanisms operate when environmental variation favors different species at different times. 
Under the storage effect, this happens because species are competing for resources at different times (and escaping competition in unfavorable periods). 
Under relative nonlinearity, all species are competing for resources at the same time, but each species alters resource availability in a way that favors its competitors.
We describe these mechanisms in more detail below (see \textbf{Materials and Methods: Consumer-resource model}).}

@@

\begin{align}
  D_{i,\tau(0) + 1} &= (1-\gamma_{i,\tau}) \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  N_{i,\tau(0) + 1} &= \gamma_{i,\tau} \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  R_{\tau(0) + 1} &= \text{lognormal}\left(\mu(R^+), \sigma(R^+) \right)_0^{200},
\end{align}\vspace{-3em}
